---
title: "Week4_Project"
author: "Kumiko Urgent"
date: "8/16/2020"
output: ioslides_presentation
---

```{r}
library(UsingR)
```

## Overview

This presentation shows how to use an application, "Price Prediction for a diamond".
The Diamonds data set from *UsingR* package was used.  Approximately 54,000 diamonds and their characteristics are in this data set.  The variables are **price**, **size (in carat)**, **type of cut**, **color**,**clarity**,**length (x)**,**width(y)**, and **depth(z)**.

Price was predicted using a linear regression with three variables: carat, cut and color.



## Dataset Detail
```{r,echo=FALSE,comment=""}
dim(diamonds)
head(diamonds)
```

## Model
A linear regression model using three variables, carat, cut and color was used for the prediction.
```{r,echo=FALSE,comment=""}
fit <- lm(price ~ I(carat-mean(carat)) + cut + color, data = diamonds)
summary(fit)
```

## Input required

- carat: You can put any size of a diamond between 0.5 and 5 carat.
- cut: Five levels shown below
- color: Seven levels shown below

```{r,echo=FALSE,comment=""}
unique(diamonds$cut)
unique(diamonds$color)
```
 Click this link if you would like to know more about the color.
 [link](http://www.mlcld.com/colour.aspx) 


